%!TEX TS-program = pdflatex
\documentclass[a4paper,12pt]{article}

\usepackage{mathptmx}
\usepackage{parskip}
\usepackage[top=1.5in,left=1in,right=1in,bottom=1in]{geometry}
%\setlength{\parindent}{0pt}
%\setlength{\parskip}{\the\baselineskip}
\pagestyle{empty} 

\makeatletter
\renewcommand\@makefntext[1]{%
  \parindent 1em\noindent
  \hbox{\@makefnmark}#1}
\renewcommand\large{\@setfontsize\large{14pt}{18}} % For standardizing with the Word template: normally \large is 14.4pt
\makeatother
\usepackage{titlesec}
\titleformat{\subsection}{\normalfont\normalsize}{\thesubsection.}{1ex}{}
\titleformat{\subsubsection}{\normalfont\normalsize}{\thesubsubsection.}{1ex}{}
\titleformat{\section}{\normalfont\normalsize\bfseries}{\thesection.}{1ex}{}
\titlespacing*{\section}{0pt}{*0}{0pt}
\titlespacing*{\subsection}{0pt}{\the\baselineskip}{0pt}

\usepackage{natbib} 
\bibpunct{(}{)}{;}{a}{,}{,}

\def\bad{{\leavevmode\llap{*}}}
\def\marginal{{\leavevmode\llap{?}}}
\def\verymarginal{{\leavevmode\llap{??}}}
\def\swmarginal{{\leavevmode\llap{4}}}
\def\infelic{{\leavevmode\llap{\#}}}

\newcommand{\6}{\mbox{$[\hspace*{-.6mm}[$}} 
\newcommand{\9}{\mbox{$]\hspace*{-.6mm}]$}}
\newcommand{\sem}[2]{\6#1\9$^{#2}$}
\newcommand{\mes}[1]{\6#1\9}

\RequirePackage[hyphens]{url}
\usepackage{enumitem,xcolor,color,graphbox,amsmath,amssymb,float,subcaption,hyperref,gb4e}
%\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
%\usepackage[hyphens]{url}

\newcommand{\citepos}[1]{\citeauthor{#1}'s \citeyear{#1}}
\newcommand{\citetpos}[1]{\citeauthor{#1}'s (\citeyear{#1})}

\setlength{\bibsep}{0pt} \relax
\setcitestyle{notesep={: },yysep={, }} \relax

\begin{document}

Tonhauser, Judith, Marie-Catherine de Marneffe, Shari R.\ Speer and Jon Stevens. 2019. {\em On the information structure sensitivity of projective content}, Proceedings of {\em Sinn und Bedeutung 23}. 

\url{https://github.com/judith-tonhauser/projectivity-and-focus-sensitivity}

{\large \textbf{Appendix A \\[.2cm] Experiment materials: 108 polar questions}}


\begin{enumerate}[leftmargin=3ex,itemsep=-4pt]

\item {\bf clean}

\begin{enumerate}[leftmargin=2ex,itemsep=-4pt]
\item Did Annie stop cleaning	/ clean again / clean thoroughly when / before Pete arrived?
\item Did Bennie stop cleaning /clean again / clean thoroughly when / before Rick showed up?
\item Did Charley stop cleaning / clean again / clean thoroughly	when / before Sam came by?
\end{enumerate}

\item {\bf shout}
\begin{enumerate}[leftmargin=2ex,itemsep=-4pt]
\item Did Betty stop shouting / shout again	/ shout wildly when / before the rock show ended?
\item Did Freddy stop shouting / shout again	/ shout wildly	when / before the concert ended?
\item Did Jeanny stop shouting	/ shout again / shout wildly	when / before the protest ended?
\end{enumerate}

\item {\bf yell}
\begin{enumerate}[leftmargin=2ex,itemsep=-4pt]
\item Did Margie stop yelling	/ yell again / yell sternly	when / before the player was injured?
\item Did Nancy stop yelling / yell again / yell sternly when /	before the goalie was hurt?
\item Did Lucy stop yelling	 / yell again / yell sternly when /	before the player was struck?
\end{enumerate}


\item {\bf bark}
\begin{enumerate}[leftmargin=2ex,itemsep=-4pt]

\item Did Fido stop barking	 / bark again / bark aggressively	when / before the storm came?
\item Did Buddy stop barking / bark again / bark aggressively when /	before the mailman came?
\item Did Bella stop barking / bark again / bark aggressively	when / before the lightning struck?
\end{enumerate}


\item {\bf knock}
\begin{enumerate}[leftmargin=2ex,itemsep=-4pt]
\item Did Vinny stop knocking / knock again	 / knock quietly	when / before the bell rang?
\item Did Vicky stop knocking / knock again	 / knock quietly	when / before the phone rang?
\item Did Mickey stop knocking	 / knock again / knock quietly	when / before the alarm rang?
\end{enumerate}

\item {\bf whistle}
\begin{enumerate}[leftmargin=2ex,itemsep=-4pt]
\item  Did Daisy stop whistling	 / whistle again / whistle tunefully when /	before she left?
\item Did Maise stop whistling	/ whistle again	 / whistle tunefully when /	before she went out?
\item Did Rosie stop whistling / whistle again	/ whistle tunefully	when / before she entered?
\end{enumerate}


\item {\bf speak}
\begin{enumerate}[leftmargin=2ex,itemsep=-4pt]
\item Did Maddy stop speaking / speak again	/ speak casually when /	before her boss entered?
\item Did Zadie stop speaking	/ speak again	/ speak casually when / before the director came in?
\item Did Johnny stop speaking / speak again	/ speak casually when / before his super arrived?
\end{enumerate}


\newpage

\item {\bf walk}
\begin{enumerate}[leftmargin=2ex,itemsep=-4pt]
\item Did Lenny stop walking	/ walk again / walk slowly	when / before the sun went down?
\item Did Molly stop walking / walk again / walk slowly	when / before the rain began?
\item Did Abby stop walking	/  walk again	/ walk slowly when / before the storm started?
\end{enumerate}



\item {\bf smile}
\begin{enumerate}[leftmargin=2ex,itemsep=-4pt]
\item Did Eddie stop smiling / smile again / smile ironically when /	before the tune played?
\item Did Teddy stop smiling / smile again / smile ironically	when / before the song came on?
\item Did Danny stop smiling / smile again	/ smile ironically	when / before the band played?
\end{enumerate}


\item {\bf cry}
\begin{enumerate}[leftmargin=2ex,itemsep=-4pt]
\item Did Jamie stop crying	/ cry again	/ cry loudly when /	before the verdict came in?
\item Did Addy stop crying	/ cry again	/ cry loudly when / before the award was announced?
\item Did Katie stop crying	/ cry again	/ cry loudly when / before the prize was revealed?
\end{enumerate}


\item {\bf text} 
\begin{enumerate}[leftmargin=2ex,itemsep=-4pt]
\item Did Robbie stop texting	/ text again	/ text secretly	when / before Kim showed up?
\item Did Sophie stop texting / text again	/ text secretly	when / before Tom walked in?
\item Did Alfie stop texting  / text again	/ text secretly	when / before Dan arrived?
\end{enumerate}


\item {\bf giggle}
\begin{enumerate}[leftmargin=2ex,itemsep=-4pt]
\item Did Harry stop giggling / giggle again / giggle nervously	when / before the interview started?
\item Did Ronny stop giggling	/ giggle again	/ giggle nervously	when / before the meeting began?
\item Did Henry stop giggling / giggle again / giggle nervously	when / before the exam started?

\end{enumerate}
\end{enumerate}


\bibliographystyle{chicago}
\bibliography{/Users/tonhauser.1/Documents/bibliography}

\end{document}
